---
title: "Olist E-commerce EDA"
subtitle: "Sales Structure Analysis"
author: "Group 2"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    theme: flatly
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 9,
  fig.height = 5.6
)

library(tidyverse)
library(lubridate)
library(scales)
library(knitr)

theme_exec <- function(base_size = 12) {
  theme_minimal(base_size = base_size) +
    theme(
      plot.title = element_text(face = "bold", size = base_size + 3),
      plot.subtitle = element_text(color = "gray35"),
      panel.grid.minor = element_blank(),
      legend.position = "bottom"
    )
}

get_project_dir <- function() {
  if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::isAvailable()) {
    active_file <- rstudioapi::getActiveDocumentContext()$path
    if (!is.null(active_file) && nzchar(active_file)) return(dirname(active_file))
  }
  getwd()
}
```

```{r data-prep, include=FALSE}
project_dir <- get_project_dir()
data_dir <- file.path(project_dir, "olist dataset")

if (!dir.exists(data_dir)) {
  stop("Data folder not found: ", data_dir)
}

customers <- read_csv(file.path(data_dir, "olist_customers_dataset.csv"))
geolocation <- read_csv(file.path(data_dir, "olist_geolocation_dataset.csv"))
order_items <- read_csv(file.path(data_dir, "olist_order_items_dataset.csv"))
payments <- read_csv(file.path(data_dir, "olist_order_payments_dataset.csv"))
reviews <- read_csv(file.path(data_dir, "olist_order_reviews_dataset.csv"))
orders <- read_csv(file.path(data_dir, "olist_orders_dataset.csv"))
products <- read_csv(file.path(data_dir, "olist_products_dataset.csv"))
sellers <- read_csv(file.path(data_dir, "olist_sellers_dataset.csv"))
translations <- read_csv(file.path(data_dir, "product_category_name_translation.csv"))

item_sales_data <- order_items %>%
  left_join(products, by = "product_id") %>%
  left_join(translations, by = "product_category_name") %>%
  left_join(orders, by = "order_id") %>%
  mutate(
    category = coalesce(product_category_name_english, product_category_name, "unknown"),
    clean_category = str_to_title(str_replace_all(category, "_", " ")),
    order_purchase_timestamp = ymd_hms(order_purchase_timestamp),
    order_delivered_customer_date = ymd_hms(order_delivered_customer_date),
    order_estimated_delivery_date = ymd_hms(order_estimated_delivery_date)
  )

clean_reviews <- reviews %>%
  filter(!is.na(review_score)) %>%
  group_by(order_id) %>%
  summarise(review_score = mean(review_score), .groups = "drop")

top_20_volume <- item_sales_data %>%
  filter(!is.na(product_category_name_english)) %>%
  count(category, clean_category, name = "total_purchased", sort = TRUE) %>%
  slice_head(n = 20)

top_20_status_analysis <- item_sales_data %>%
  semi_join(top_20_volume, by = c("category", "clean_category")) %>%
  group_by(category, clean_category) %>%
  summarise(
    total_purchased = n(),
    delivered_count = sum(order_status == "delivered", na.rm = TRUE),
    failed_count = sum(order_status %in% c("canceled", "unavailable"), na.rm = TRUE),
    failure_rate_pct = failed_count / total_purchased,
    .groups = "drop"
  ) %>%
  arrange(desc(total_purchased))

top_category <- top_20_status_analysis %>% slice_max(total_purchased, n = 1)
highest_failure <- top_20_status_analysis %>% slice_max(failure_rate_pct, n = 1)
```

## Objective

The objective is to study the top performers and the products Olist has been struggling to sell.

## 1. Sales Volume and Order Status

```{r top-volume-plot}
top_20_status_analysis %>%
  mutate(clean_category = fct_reorder(clean_category, total_purchased)) %>%
  ggplot(aes(x = total_purchased, y = clean_category)) +
  geom_col(fill = "#276b62", width = 0.72) +
  geom_text(aes(label = comma(total_purchased)), hjust = -0.12, size = 3) +
  scale_x_continuous(labels = comma, expand = expansion(mult = c(0, 0.14))) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Top 20 Most Purchased Categories",
    subtitle = "By total order-item rows",
    x = "Items purchased",
    y = NULL
  ) +
  theme_exec()
```

```{r failure-rate-plot}
top_20_status_analysis %>%
  mutate(clean_category = fct_reorder(clean_category, failure_rate_pct)) %>%
  ggplot(aes(x = failure_rate_pct, y = clean_category)) +
  geom_col(fill = "#a65345", width = 0.72) +
  geom_text(aes(label = percent(failure_rate_pct, accuracy = 0.1)), hjust = -0.12, size = 3) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.18))) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Cancellation and Failure Rate",
    subtitle = "Failure rate among top 20 categories",
    x = "Failure rate",
    y = NULL
  ) +
  theme_exec()
```

**Interpretation:** High volume identifies commercial demand. Failure rate shows where demand may be leaking because orders are canceled or unavailable.

## 2. Review Sentiment

```{r sentiment-prep, include=FALSE}
sentiment_colors <- c(
  "Positive (4-5 Stars)" = "#4CAF50",
  "Neutral (3 Stars)" = "#9E9E9E",
  "Negative (1-2 Stars)" = "#F44336"
)

sentiment_analysis <- item_sales_data %>%
  semi_join(top_20_volume, by = c("category", "clean_category")) %>%
  inner_join(clean_reviews, by = "order_id") %>%
  mutate(sentiment = case_when(
    review_score >= 4 ~ "Positive (4-5 Stars)",
    review_score >= 2.5 ~ "Neutral (3 Stars)",
    TRUE ~ "Negative (1-2 Stars)"
  )) %>%
  count(clean_category, sentiment, name = "review_count") %>%
  group_by(clean_category) %>%
  mutate(percent = review_count / sum(review_count)) %>%
  ungroup()
```

```{r sentiment-plot}
sentiment_analysis %>%
  ggplot(aes(x = fct_reorder(clean_category, percent), y = percent, fill = sentiment)) +
  geom_col(width = 0.72) +
  coord_flip() +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = sentiment_colors) +
  labs(
    title = "Review Sentiment by Top 20 Categories",
    subtitle = "Deduplicated order reviews",
    x = NULL,
    y = "Share of reviews",
    fill = "Sentiment"
  ) +
  theme_exec()
```

**Interpretation:** Sentiment adds customer experience context to volume. A category can sell well but still create dissatisfaction. From the plot we see that Furniture categories (office and decor) have the highest percentage of negative reviews which would require further analysis.

## 3. Geographic Concentration

```{r geo-prep, include=FALSE}
geo_analysis <- item_sales_data %>%
  semi_join(top_20_volume, by = c("category", "clean_category")) %>%
  left_join(customers, by = "customer_id") %>%
  count(clean_category, customer_state, name = "items_sold") %>%
  group_by(clean_category) %>%
  mutate(percent_of_category = items_sold / sum(items_sold)) %>%
  ungroup()
```

```{r geo-plot, fig.width=11, fig.height=7}
geo_analysis %>%
  ggplot(aes(x = customer_state, y = clean_category, fill = percent_of_category)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "#ebf4f6", high = "#08306b", labels = percent) +
  labs(
    title = "Geographic Concentration of Top Categories",
    subtitle = "Share of category sales by Brazilian state",
    x = "Customer state",
    y = NULL,
    fill = "% of category"
  ) +
  theme_exec() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), panel.grid = element_blank())
```

**Interpretation:** Geographic concentration helps Sales decide where to focus seller coverage, stock placement and logistics improvement. From the plots, we see San Paolo has the most orders followed by MG, and RJ.

## 4. Macro Segments and Revenue

```{r macro-revenue-prep, include=FALSE}
segment_data <- item_sales_data %>%
  filter(!is.na(product_category_name_english)) %>%
  mutate(macro_segment = case_when(
    category %in% c("bed_bath_table", "furniture_decor", "housewares", "home_confort", "office_furniture", "home_construction") ~ "Home & Furniture",
    category %in% c("health_beauty", "perfumery", "fashion_bags_accessories", "watches_gifts", "luggage_accessories") ~ "Fashion & Beauty",
    category %in% c("computers_accessories", "telephony", "electronics", "consoles_games", "pc_gamer", "audio") ~ "Tech & Electronics",
    category %in% c("sports_leisure", "auto", "garden_tools", "toys", "musical_instruments") ~ "Sports, Auto & Leisure",
    category %in% c("baby", "stationery", "pet_shop", "books_general_interest") ~ "Family, Pets & Hobbies",
    TRUE ~ "Other/Miscellaneous"
  )) %>%
  count(macro_segment, name = "total_items_sold", sort = TRUE) %>%
  mutate(market_share_pct = total_items_sold / sum(total_items_sold))

revenue_data <- item_sales_data %>%
  filter(!is.na(product_category_name_english)) %>%
  group_by(category, clean_category) %>%
  summarise(
    total_revenue = sum(price, na.rm = TRUE),
    total_volume = n(),
    average_price = mean(price, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(total_revenue)) %>%
  slice_head(n = 20)
```

```{r macro-plot}
segment_data %>%
  mutate(macro_segment = fct_reorder(macro_segment, total_items_sold)) %>%
  ggplot(aes(x = total_items_sold, y = macro_segment)) +
  geom_col(fill = "#2CA02C", width = 0.72) +
  geom_text(aes(label = percent(market_share_pct, accuracy = 0.1)), hjust = -0.12, size = 3) +
  scale_x_continuous(labels = comma, expand = expansion(mult = c(0, 0.14))) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Macro-Segment Market Share",
    subtitle = "Category groups converted into high-level departments",
    x = "Items sold",
    y = NULL
  ) +
  theme_exec()
```

```{r revenue-volume-plot}
revenue_data %>%
  ggplot(aes(x = total_volume, y = total_revenue)) +
  geom_point(color = "#276b62", size = 3.5, alpha = 0.75) +
  geom_text(aes(label = clean_category), vjust = -0.9, size = 3, check_overlap = TRUE) +
  scale_x_continuous(labels = comma) +
  scale_y_continuous(labels = label_dollar(prefix = "R$ ")) +
  labs(
    title = "Top Revenue Categories: Revenue vs. Volume",
    subtitle = "Separates volume drivers from value-heavy categories",
    x = "Items sold",
    y = "Item revenue"
  ) +
  theme_exec()
```

## 5. Freight Burden and Weak-Category Diagnostics

```{r diagnostics-prep, include=FALSE}
logistics_analysis <- item_sales_data %>%
  semi_join(top_20_volume, by = c("category", "clean_category")) %>%
  group_by(category, clean_category) %>%
  summarise(
    total_product_revenue = sum(price, na.rm = TRUE),
    total_freight_cost = sum(freight_value, na.rm = TRUE),
    avg_price = mean(price, na.rm = TRUE),
    avg_freight = mean(freight_value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(freight_burden_pct = total_freight_cost / total_product_revenue) %>%
  arrange(desc(freight_burden_pct))

all_volume <- item_sales_data %>%
  filter(!is.na(product_category_name_english)) %>%
  count(category, clean_category, name = "total_purchased", sort = TRUE)

target_categories <- bind_rows(
  all_volume %>% slice_head(n = 20) %>% mutate(performance_group = "Top 20 Categories"),
  all_volume %>% slice_tail(n = 20) %>% mutate(performance_group = "Bottom 20 Categories")
)

review_comparison <- item_sales_data %>%
  inner_join(target_categories, by = c("category", "clean_category")) %>%
  inner_join(clean_reviews, by = "order_id") %>%
  mutate(sentiment = case_when(
    review_score >= 4 ~ "Positive (4-5 Stars)",
    review_score >= 2.5 ~ "Neutral (3 Stars)",
    TRUE ~ "Negative (1-2 Stars)"
  )) %>%
  count(clean_category, performance_group, sentiment, name = "review_count") %>%
  group_by(clean_category, performance_group) %>%
  mutate(percent = review_count / sum(review_count)) %>%
  ungroup()

negative_sort <- review_comparison %>%
  filter(sentiment == "Negative (1-2 Stars)") %>%
  select(clean_category, negative_pct = percent)

review_comparison <- review_comparison %>%
  left_join(negative_sort, by = "clean_category") %>%
  mutate(negative_pct = replace_na(negative_pct, 0))
```

```{r freight-burden-plot}
logistics_analysis %>%
  mutate(clean_category = fct_reorder(clean_category, freight_burden_pct)) %>%
  ggplot(aes(x = freight_burden_pct, y = clean_category)) +
  geom_col(fill = "#c48a2c", width = 0.72) +
  geom_text(aes(label = percent(freight_burden_pct, accuracy = 0.1)), hjust = -0.12, size = 3) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.16))) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Logistics Friction by Category",
    subtitle = "Freight cost as a share of item price",
    x = "Freight burden",
    y = NULL
  ) +
  theme_exec()
```

```{r review-comparison-plot, fig.width=11, fig.height=8}
review_comparison %>%
  ggplot(aes(x = fct_reorder(clean_category, negative_pct), y = percent, fill = sentiment)) +
  geom_col(width = 0.72) +
  coord_flip() +
  facet_wrap(~ performance_group, scales = "free_y") +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = sentiment_colors) +
  labs(
    title = "Review Sentiment: Top 20 vs. Bottom 20 Categories",
    subtitle = "Sorted by negative review share",
    x = NULL,
    y = "Share of reviews",
    fill = "Sentiment"
  ) +
  theme_exec() +
  theme(axis.text.y = element_text(size = 7.5), panel.spacing = unit(2, "lines"))
```

## 6. Delivery, Seller and Seasonality Diagnostics

```{r delivery-seasonality-prep, include=FALSE}
delivery_trends <- item_sales_data %>%
  inner_join(target_categories, by = c("category", "clean_category")) %>%
  filter(order_status == "delivered", !is.na(order_delivered_customer_date), !is.na(order_purchase_timestamp)) %>%
  mutate(delivery_days = as.numeric(difftime(order_delivered_customer_date, order_purchase_timestamp, units = "days"))) %>%
  filter(delivery_days >= 0, delivery_days <= 100)

statistical_summary <- item_sales_data %>%
  inner_join(target_categories, by = c("category", "clean_category")) %>%
  inner_join(clean_reviews, by = "order_id") %>%
  filter(!is.na(order_delivered_customer_date), !is.na(order_purchase_timestamp), !is.na(price), price > 0) %>%
  mutate(
    delivery_days = as.numeric(difftime(order_delivered_customer_date, order_purchase_timestamp, units = "days")),
    freight_ratio = freight_value / price
  ) %>%
  select(review_score, delivery_days, freight_ratio) %>%
  drop_na()

cor_matrix <- cor(statistical_summary, method = "spearman")

seller_accountability <- item_sales_data %>%
  inner_join(target_categories %>% filter(performance_group == "Bottom 20 Categories"), by = c("category", "clean_category")) %>%
  filter(!is.na(order_delivered_customer_date), !is.na(order_purchase_timestamp)) %>%
  mutate(delivery_days = as.numeric(difftime(order_delivered_customer_date, order_purchase_timestamp, units = "days"))) %>%
  group_by(clean_category, seller_id) %>%
  summarise(
    total_items_sold = n(),
    avg_delivery_days = mean(delivery_days, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(total_items_sold > 10) %>%
  arrange(desc(avg_delivery_days))

seasonality_trends <- item_sales_data %>%
  filter(!is.na(order_delivered_customer_date), !is.na(order_purchase_timestamp)) %>%
  mutate(
    purchase_month = floor_date(order_purchase_timestamp, "month"),
    delivery_days = as.numeric(difftime(order_delivered_customer_date, order_purchase_timestamp, units = "days"))
  ) %>%
  group_by(purchase_month) %>%
  summarise(
    total_orders = n(),
    avg_delivery_time = mean(delivery_days, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(total_orders > 100)
```

```{r delivery-boxplot, fig.width=11, fig.height=8}
delivery_trends %>%
  ggplot(aes(x = fct_reorder(clean_category, delivery_days, .fun = median), y = delivery_days, fill = performance_group)) +
  geom_boxplot(outlier.size = 0.5, outlier.alpha = 0.3, alpha = 0.75) +
  coord_flip() +
  facet_wrap(~ performance_group, scales = "free_y") +
  scale_fill_manual(values = c("Top 20 Categories" = "#1F77B4", "Bottom 20 Categories" = "#FF7F0E")) +
  labs(
    title = "Actual Delivery Time Distribution",
    subtitle = "Top vs. bottom categories",
    x = NULL,
    y = "Days to deliver"
  ) +
  theme_exec() +
  theme(legend.position = "none", axis.text.y = element_text(size = 7.5))
```

```{r correlation-table}
as_tibble(cor_matrix, rownames = "Metric") %>%
  kable(digits = 3)
```

```{r seller-table}
seller_accountability %>%
  slice_head(n = 20) %>%
  mutate(avg_delivery_days = round(avg_delivery_days, 1)) %>%
  kable()
```

```{r seasonality-plot}
seasonality_trends %>%
  ggplot(aes(x = purchase_month)) +
  geom_col(aes(y = total_orders), fill = "#E0E0E0", alpha = 0.75) +
  geom_line(aes(y = rescale(avg_delivery_time, to = range(total_orders))), color = "#D32F2F", linewidth = 1.1) +
  geom_point(aes(y = rescale(avg_delivery_time, to = range(total_orders))), color = "#D32F2F", size = 2) +
  scale_x_date(date_labels = "%Y-%m", date_breaks = "2 months") +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Supply Chain Stress Test",
    subtitle = "Order volume bars with scaled average delivery-time line",
    x = "Purchase month",
    y = "Order volume"
  ) +
  theme_exec() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## 7. Transaction Clustering

```{r transaction-clustering}
if (requireNamespace("cluster", quietly = TRUE)) {
  ml_data <- item_sales_data %>%
    filter(!is.na(price), !is.na(freight_value), !is.na(order_delivered_customer_date), !is.na(order_purchase_timestamp)) %>%
    mutate(delivery_days = as.numeric(difftime(order_delivered_customer_date, order_purchase_timestamp, units = "days"))) %>%
    select(order_id, price, freight_value, delivery_days) %>%
    filter(price < 1000, freight_value < 100, delivery_days > 0, delivery_days < 60) %>%
    drop_na()

  scaled_features <- ml_data %>%
    select(price, freight_value, delivery_days) %>%
    scale()

  set.seed(42)
  kmeans_model <- kmeans(scaled_features, centers = 3, nstart = 25)

  ml_data <- ml_data %>% mutate(cluster_id = factor(kmeans_model$cluster))

  cluster_summary <- ml_data %>%
    group_by(cluster_id) %>%
    summarise(
      total_sales = n(),
      avg_price = mean(price),
      avg_freight = mean(freight_value),
      avg_delivery_days = mean(delivery_days),
      freight_burden_pct = mean(freight_value) / mean(price),
      .groups = "drop"
    )

  cluster_summary %>%
    mutate(
      avg_price = label_dollar(prefix = "R$ ", accuracy = 1)(avg_price),
      avg_freight = label_dollar(prefix = "R$ ", accuracy = 1)(avg_freight),
      avg_delivery_days = round(avg_delivery_days, 1),
      freight_burden_pct = percent(freight_burden_pct, accuracy = 0.1)
    ) %>%
    kable()
}
```

```{r transaction-clustering-plot}
if (exists("ml_data")) {
  ml_data %>%
    ggplot(aes(x = price, y = freight_value, color = cluster_id)) +
    geom_point(alpha = 0.35, size = 1.2) +
    scale_color_manual(values = c("1" = "#4CAF50", "2" = "#FFC107", "3" = "#F44336")) +
    labs(
      title = "K-means Transaction Segmentation",
      subtitle = "Operational profiles based on price, freight and delivery days",
      x = "Product price (R$)",
      y = "Freight cost (R$)",
      color = "Cluster"
    ) +
    theme_exec()
}
```


## Business Takeaways
-   **Weak categories need diagnosis:** low volume may come from demand, but also from freight friction, reviews, delivery delays or seller issues.
-   **Freight burden is a sales lever:** categories where shipping is high relative to product price may benefit from bundling, minimum-order thresholds or logistics renegotiation.
-   **Customer experience matters:** review sentiment and delivery variance should be evaluated alongside sales volume before making assortment decisions.
